### 2018-04-29 paper/design.tex

The privacy objectives of our system require encryption primitives that we first detail in section~\ref{BuildingBlocks}. The other constituents of \name are depicted in figure~\ref{fig:outline}.
On top, the devices of each user are circled in gray, and form a user's device squad. The squad online members communicate among themselves: they exchange files and messages information, and cooperate to predict the user's future behavior. This first protocol is called the \emph{Squad Overlay} and will be discussed in section~\ref{sec:squad_overlay}.
%On top we see that each user's devices (shown as clouds) communicate with one another through a dissemination protocol---coined the \emph{squad overlay}---that will be discussed in section~\ref{sec:squad_overlay}. 
Below, we see all devices connected in a random graph: each device gives information about itself to random nodes when it is online. 
This \emph{Global Overlay} will be covered in section~\ref{sec:global_overlay}.
The information brought by these overlays allows devices to securely and reliably exchange messages between users, as will be explained in section~\ref{sec:message_passing}.
Given this message passing protocol, users can privately exchange files, as shown in the bottom of the figure. We will cover this ultimate goal in section~\ref{sec:file_exchange}.

\begin{figure}[t]
\centering
\def\svgwidth{\columnwidth}
%\input{outline.pdf_tex}
\import{figures/}{outline.pdf_tex}
%\includegraphics[width=0.9\columnwidth]{figures/outline.pdf}
\caption{\label{fig:outline}Outline of \name's components.}

\end{figure}

>>>>

\begin{figure}[t]
\centering
\def\svgwidth{\columnwidth}
%\input{outline.pdf_tex}
\import{figures/}{outline.pdf_tex}
%\includegraphics[width=0.9\columnwidth]{figures/outline.pdf}
\caption{\label{fig:outline}Outline of \name's components. Users squads of devices are circled in gray. From top to bottom: a user's devices collaborate through the Squad Overlay; online devices globally share information about them to random peers; using the two above overlays allows for the creation or Predictive Onion Routes (PORs) between sets of devices; secure file exchange between users is enabled by PORs.}
\end{figure}

The privacy objectives of our system require encryption primitives that we first detail in section~\ref{BuildingBlocks}. The other constituents of \name are depicted in figure~\ref{fig:outline}.
On top, the devices of each user are circled in gray, and form a user's device squad. The squad online members communicate among themselves: they exchange files and messages information, and cooperate to predict the user's future behavior. 
This first protocol is called the \emph{Squad Overlay} and will be discussed in section~\ref{sec:squad_overlay}.
%On top we see that each user's devices (shown as clouds) communicate with one another through a dissemination protocol---coined the \emph{squad overlay}---that will be discussed in section~\ref{sec:squad_overlay}. 
Below, we see all devices connected in a random graph: each device gives information about itself to random nodes when it is online. 
This \emph{Global Overlay} will be covered in section~\ref{sec:global_overlay}.
The information brought by these overlays allows devices to securely and reliably exchange messages between users by creating Predictive Onion Routes (PORs), as will be explained in section~\ref{sec:message_passing}.
Given this message passing protocol, users can privately exchange files, as shown in the bottom of the figure. We will cover this ultimate goal in section~\ref{sec:file_exchange}.
